Library-based fault tolerance for scientific applications

### 2013-01-07 paper.tex
Added two experiments-to-do

\greg{This section needs performance results. How much slower are the resilient routines and how much more resilient do they become across a range of detection thresholds.}

@@

\paragraph{Cholesky Decomposition}: \greg{Need to define this decomposition}
By multiplying back the upper and lower halves, the checker takes as much time as a regular matrix-matrix multiplication would do. The original routine is an iterative one, but it generally runs longer than the checker. \greg{How much longer? Need to quantify.}

@@

\greg{This is the section where we put all the pieces together and present the experimental results on full applications. We should describe our main use-case here: user wants to achieve a given accuracy with a given probability and we configure the algorithm to provide this at the lowest cost. QUESTION: how do we pick the parameters of each resilience technique? Which metric is being optimized?}

>>>>

\greg{This section needs performance results. How much slower are the resilient routines and how much more resilient do they become across a range of detection thresholds.}
\sui{Performance experiments inserted here: running algorithmic checkers across different input sizes and fault rates: 62x62 to 500x500 matrixes for MM, RK, CD, MV checkers; FFT sizes of $2^8$ to $2^{24}$ for the FFT checker; Error bars should apply here, especially for the Cholesky Decomposition checker}

@@

\paragraph{Cholesky Decomposition}: \greg{Need to define this decomposition}
By multiplying back the upper and lower halves, the checker takes as much time as a regular matrix-matrix multiplication would do. The original routine is an iterative one, but it generally runs longer than the checker. \greg{How much longer? Need to quantify.} \sui{Can we quantify it using the performance data?}

@@

\greg{This is the section where we put all the pieces together and present the experimental results on full applications. We should describe our main use-case here: user wants to achieve a given accuracy with a given probability and we configure the algorithm to provide this at the lowest cost. QUESTION: how do we pick the parameters of each resilience technique? Which metric is being optimized?} \sui{Using the choices of those parameters derived from the experiments we have already performed (treat it as a ``training set'') and use those choices on some new experiment configurations (treat as ``test set''), and see what is the probability that those choices could satisfy the users' experiments.}
